%-------------------------
% Resume in Latex (Fixed & ATS Friendly)
% Author : Shiv Shankar Singh (based on Jake Gutierrez template)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Page setup
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure ATS readability
\pdfgentounicode=1

% Commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Shiv Shankar Singh} \\ \vspace{4pt}
    \small +91-7068900427 $|$ \href{mailto:singhshiv0427@gmail.com}{singhshiv0427@gmail.com} $|$
    \href{https://www.linkedin.com/in/shiv-shankar-singh-/}{linkedin.com/in/shiv-shankar-singh} $|$
    \href{https://github.com/sh1v-max}{github.com/sh1v-max}
\end{center}

%-----------SUMMARY-----------
\section{Professional Summary}
Aspiring Frontend Developer skilled in \textbf{React.js, JavaScript (ES6+), HTML5, CSS3, Redux, and REST APIs}. Experienced in building responsive, user-focused applications with strong knowledge of modern UI frameworks, state management, and testing libraries. Passionate about performance optimisation and clean, maintainable code.

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Lovely Professional University}{Punjab, India}
    {B.Tech. in Computer Science and Engineering}{Oct 2020 -- Jul 2024}
  \resumeSubheading
    {Tulsi Vidya Niketan}{Varanasi, India}
    {Higher Secondary (CBSE Board) -- 83\%}{Mar 2018 -- Jul 2020}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
  \resumeSubheading{NetflixGPT}{React.js, Redux Toolkit, Firebase, REST APIs, Tailwind CSS}
  {Streaming Web App}{}
    \begin{itemize}[leftmargin=0.3in]
      \resumeItem{Built a movie streaming platform with \textbf{AI-driven search}, custom hooks, and reusable components.}
      \resumeItem{Integrated \textbf{Firebase authentication} and TMDB API for categories and trailers.}
      \resumeItem{Optimized performance using memoization, reducing API latency by 25\% and improving load time by 30\%.}
      \resumeItem{Deployed on Firebase Hosting with \textbf{95\% mobile compatibility}.}
    \end{itemize}

  \resumeSubheading{BiteSwift}{React.js, Redux, REST APIs, Tailwind CSS, Auth0}
  {Food Delivery Platform}{}
    \begin{itemize}[leftmargin=0.3in]
      \resumeItem{Developed responsive restaurant app with dynamic homepage, cart management, and search.}
      \resumeItem{Implemented lazy loading, sessionStorage, and custom hooks to minimize reloads and improve UX.}
      \resumeItem{Achieved 100\% mobile compatibility and reduced navigation time by 25\%.}
    \end{itemize}

  \resumeSubheading{Portfolio}{React.js, Tailwind CSS, Context API, Netlify}
  {Personal Developer Website}{}
    \begin{itemize}[leftmargin=0.3in]
      \resumeItem{Designed and deployed personal portfolio showcasing skills and projects.}
      \resumeItem{Integrated EmailJS for real-time form submissions without backend.}
    \end{itemize}

  \resumeSubheading{YourCountry}{React.js, REST APIs, Hooks}
  {Country Info Webpage}{}
    \begin{itemize}[leftmargin=0.3in]
      \resumeItem{Built a country information app displaying country details and neighbors via REST APIs.}
      \resumeItem{Optimized data fetching with hooks, improving performance by 30\% and ensuring 100\% responsiveness.}
    \end{itemize}
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{Languages:} JavaScript (ES6+), HTML5, CSS3 \\
    \item \textbf{Frameworks/Libraries:} React.js, Redux, Context API, Tailwind CSS, Firebase, RESTful APIs \\
    \item \textbf{Tools:} Git, GitHub, npm, Babel, Parcel, Netlify, Firebase Hosting \\
    \item \textbf{Others:} Testing (React Testing Library, Vitest), OOP, DBMS, Linux
\end{itemize}

%-----------CERTIFICATIONS-----------
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item The Complete 2023 Web Development Bootcamp (Udemy) -- Jul 2023 
    \item Server-side JavaScript with Node.js (Coursera) -- May 2023
    \item Data Structures and Algorithms - Self Paced (GeeksforGeeks) -- Jul 2022
    \item Introduction to Programming Using Java (Coding Ninjas) -- May 2022
\end{itemize}

\end{document}
